
---
title: "Jar History"
output:
 html_document:
    df_print: paged
    code_folding: hide
    toc: TRUE
    toc_depth: 4
    toc_float: true
    theme: cerulean
    highlight: haddock
    smart: false
editor_options: 
  chunk_output_type: inline
---


Hello World

Author: OA Lab, NWFSC
Title: Reading Meta data for Krill Towing Data
Date: October 2021



# Version Check
```{r 0.1 Version Check , echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
## Version Check
#********************************* 
R.version

```




# 1.) Libraries
```{r 0.0 Libraries , echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
##Libraries
#********************************* 
library(stringr)
library(tidyverse)
library(plyr)
library(nlme)
library(tidyr)
library(dbplyr)
library(dplyr)
library(purrr)
library(wql)
library(lubridate)
library(tibbletime)
#for graphing
library(ggplot2)
library(ggeasy)
library(ggfortify)
library(stringr)
library(nlme)
library(RColorBrewer)
library(patchwork)
#statistical analysis
# library(gdata)
# library(rsq)
# library(doBy)
# library(lme4)
# library(lmerTest)
#Rnotebooks 
library(gridExtra)
library(kableExtra)
library(todor)
library(knitr)
#metadata
library(metacsv)
#Hydrogen concentration
library(seacarb)

```



# 2.) Creating Dataframes and new CSV documents 
```{r Creating Dataframes and new CSV documents }

#*********************************
## 2.) Creating Dataframes and new CSV documents
#*********************************

jarSalinity <- read_csv(here::here("Data", "jar_History.csv"))

 
```


# Summary Groups of Salinity Start & End by Bottle ID
The start doesn't truly need a mean since since Bottle has a unique salinity
```{r}

#Summary of Salinity by Bottle Cohorts- Bottle IDs

jarSalinity_Start.summary <- jarSalinity %>% group_by(BottleID) %>%
  dplyr::summarize(sd = sd(SourceSalinity, na.rm = TRUE), 
            mean = mean(SourceSalinity, na.rm = TRUE), 
            median = median(SourceSalinity, na.rm = TRUE),
            IQR = IQR(SourceSalinity, na.rm = TRUE),
            n = n()) %>%
  mutate(se = sd/sqrt(n)) %>%
  mutate(ci = se*1.96)
jarSalinity_Start.summary  


jarSalinity_End.summary <- jarSalinity %>% group_by(BottleID) %>%
  dplyr::summarize(sd = sd(BubbleEndSalinity, na.rm = TRUE), 
            mean = mean(BubbleEndSalinity, na.rm = TRUE), 
            median = median(BubbleEndSalinity, na.rm = TRUE),
            IQR = IQR(BubbleEndSalinity, na.rm = TRUE),
            n = n()) %>%
  mutate(se = sd/sqrt(n)) %>%
  mutate(ci = se*1.96)
jarSalinity_End.summary 


```

# Chamber 09 Salinity Changes
```{r}

jarSalinity$Salinity_Delta <- ""
jarSalinity$Salinity_Delta <- jarSalinity$BubbleEndSalinity-jarSalinity$SourceSalinity

jarSalinity <- jarSalinity %>%
  dplyr::rename(insertType = id_2)


Chamber09bottles = subset(jarSalinity, unit_ID == "Chamber_9")


CH09_s_plot1 <- ggplot(Chamber09jars, aes(BottleID, Salinity_Delta)) +
            # geom_jitter(color = "grey") +
            geom_point(data = Chamber09jars, 
                       aes(BottleID, Salinity_Delta)) +
            facet_wrap(~treatment) +
            xlab("Jar and Bottle ID") +
            ylab("Salinity (measured before and after 1hr bubbling") +
            ggtitle("Salinity Difference (CH09)") +
            theme_bw() 

CH09_s_plot1
p9a <- CH09_s_plot1+ theme(axis.text=element_text(size=5),
        axis.title=element_text(size=7,face="bold"))
p9a + theme(axis.text.x = element_text(angle = 30))

# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - | 

# salinity_plot1 <- ggplot(jarSalinity, aes(JarID, Salinity_Delta)) +
#             # geom_jitter(color = "grey") +
#             geom_point(data = jarSalinity, 
#                        aes(BottleID, Salinity_Delta)) +
#             # geom_point(data = jarSalinity, 
#             #            aes(JarID, Salinity_Delta), colour = insertType) +
#             facet_wrap(~treatment) +
#             xlab("Bottle ID") +
#             ylab("Salinity (measured before and after 1hr bubbling") +
#             ggtitle("Salinity Change from Source Bottle") +
#             theme_bw() 
# 
# salinity_plot1
# salinity_plot1 + theme(axis.text.x = element_text(angle = 30))


# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

# p<-ggplot(data=jarSalinity, aes(x=BottleID, y=SourceSalinity)) +
#   geom_bar(stat="jarSalinity")
# p






```


# Chamber 10 Salinity Changes
```{r}

Chamber10bottles = subset(jarSalinity, unit_ID == "Chamber_10")


CH10_s_plot1 <- ggplot(Chamber10bottles, aes(BottleID, Salinity_Delta)) +
            # geom_jitter(color = "grey") +
            geom_point(data = Chamber10bottles, 
                       aes(BottleID, Salinity_Delta)) +
            facet_wrap(~treatment) +
            xlab("Jar and Bottle ID") +
            ylab("Salinity (measured before and after 1hr bubbling") +
            ggtitle("Salinity Difference (CH10)") +
            theme_bw() 

CH10_s_plot1
p10a <- CH10_s_plot1+ theme(axis.text=element_text(size=5),
        axis.title=element_text(size=7,face="bold"))
p10a + theme(axis.text.x = element_text(angle = 30))

# - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - | 


```






#**************E*N*D*************# 
#*********************************
## END OF SCRIPT | END OF DOCUMENT 
#*********************************
```


## END OF SCRIPT | END OF DOCUMENT





