
---
title: "Jar leak Test"
output:
 html_document:
    df_print: paged
    code_folding: hide
    toc: TRUE
    toc_depth: 4
    toc_float: true
    theme: cerulean
    highlight: haddock
    smart: false
editor_options: 
  chunk_output_type: inline
---


Hello World

Author: OA Lab, NWFSC
Title: Reading Meta data for Krill Towing Data
Date: September 2021


# Version Check
```{r 0.1 Version Check , echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
## Version Check
#********************************* 
R.version

```



# 1.) Libraries
```{r 0.0 Libraries , echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
##Libraries
#********************************* 
library(stringr)
library(tidyverse)
library(plyr)
library(nlme)
library(tidyr)
library(dbplyr)
library(dplyr)
library(purrr)
library(wql)
library(lubridate)
library(tibbletime)
#for graphing
library(ggplot2)
library(ggeasy)
library(ggfortify)
library(stringr)
library(nlme)
library(RColorBrewer)
library(patchwork)
#statistical analysis
# library(gdata)
# library(rsq)
# library(doBy)
# library(lme4)
# library(lmerTest)
#Rnotebooks 
library(gridExtra)
library(kableExtra)
library(todor)
library(knitr)
#metadata
library(metacsv)
#Hydrogen concentration
library(seacarb)

```



# 2.) Creating Dataframes and new CSV documents 
```{r Creating Dataframes and new CSV documents }

#*********************************
## 2.) Creating Dataframes and new CSV documents
#*********************************

jarTest <- read_csv(here::here("raw_Data", "jarLeak", "SpecData_Cohort_1_to_8_Day00Day03.csv"))
bottleMAP <- read_csv(here::here("raw_Data", "jarLeak", "BottleSalinityMap.csv"))
jarMAP <- read_csv(here::here("raw_Data", "jarLeak", "jarBottleMap.csv"))

repeatability <- read_csv(here::here("Data", "SpecData_Repeatability_compare.csv"))
rpt_cohort1 <- read_csv(here::here("Data", "TRISround1_round2_cohort1.csv"))
rpt_cohort2 <- read_csv(here::here("Data", "TRISround1_round2_cohort2.csv"))
rpt_cohort3 <- read_csv(here::here("Data", "TRISround1_round2_cohort3.csv"))
rpt_map <- read_csv(here::here("Data", "TRISmap.csv"))

IO_val <- read_csv(here::here("Data", "InstantOceanValidations.csv"))


# TODO missing six measurements
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

```



# 3.) Data cleaning
Key points: 14 jars per Chamber
28x2 Jar Observations should be recorded
56 observations total

```{r Jar Test Cleaning}
#*********************************
## 3.) Jar Test Cleaning
#*********************************

jarTest$date <- as.POSIXct(jarTest$date, format="%m/%d/%y")
names(jarTest)
#  [1] "experiment"  "unit"        "unit_number" "id_1"        "id_2"        "id_3"        "time"        "date"       
#  [9] "salinity"    "pHat25"      "fileName"    "unit_ID"     "alk"         "insituTemp"  "pHinsitu"    "dateString" 
# [17] "treatName"   "treatpH"     "treatTemp"   "treatOther"  "dic"         "tankTemp"    "JarID"       "treatment"

# jarTest columns of interest
#  [1]  "unit"     "unit_number" "id_1"        "id_2"        "id_3"       "date"
#  [7] "salinity    "unit_ID"      "pHinsitu"     "JarID"       "treatment"
# 11 items of interest

# Jar SPEC Subelection Time!
jar_SPEC <- subset(jarTest, select = -c(experiment,
                                               time, 
                                              pHat25,
                                              fileName,
                                              treatName,
                                              treatpH, 
                                              alk,
                                              insituTemp,
                                              dateString,
                                              treatName,
                                              treatpH,
                                              treatTemp,
                                              treatOther,
                                              dic))

#Jar Map cleaning
names(jarMAP)
 # [1] "SEQ"            "Manufacturer"   "CHMBR"          "BottleTime"    
 # [5] "BottleDate"     "BottleNumber"   "JarID"          "insert"        
 # [9] "Manufacturer_1" "Treatment"

#Creating at least 6 column file -  Creating a Jar History File
# column 1 JarID
# column 2 Source Bottle
# column 3 Bottle pH Day 00
# column 4 Bootle pH Day 03
# column 5 delta of pH
# column 6 Jar Description (manufacturer and insert)

jar_History <- merge(jar_SPEC, jarMAP, by = "JarID")
# loss of observation by dropping bottles

names(jar_History)
 
# jarTest <- jarTest %>%
#   dplyr::rename(BottleID = BottleCohort)

jar_History <- jar_History %>%
  dplyr::rename(BottleID = BottleNumber)


# bottle_pH <- subset(jarTest, id_1 == "Bottle", select = c(BottleID, 
#                                                           pHinsitu))
# bottle_History <- merge(bottle_pH, bottleMAP, by = "BottleID")

jar_History <- merge(jar_History, bottleMAP, by = "BottleID")


names(jar_History)
#  [1] "BottleID"          "JarID"             "unit"              "unit_number"       "id_1"             
#  [6] "id_2"              "id_3"              "date"              "salinity"          "unit_ID"          
# [11] "pHinsitu"          "tankTemp"          "treatment"         "SEQ"               "Manufacturer"     
# [16] "CHMBR"             "BottleTime"        "BottleDate"        "insert"            "Manufacturer_1"   
# [21] "Treatment.x"       "SourceSalinity"    "BubbleEndSalinity" "Treatment.x"       "Day00_pHiinsitu"  
# [26] "X6"                "X7"                "X8"                "X9"                "X10"              
# [31] "X11"               "X12"               "X13"              

# #Cleaning if any of jar history
jar_History <- subset(jar_History, select = -c(tankTemp,
                                               Treatment.x,
                                              Treatment.x,
                                              X6,
                                              X7,
                                              X8,
                                              X9,
                                              X10,
                                              X11,
                                              X12,
                                              X13))

jar_History <- jar_History %>%
  dplyr::rename(Day03_pHinsitu = pHinsitu)


jar_History$delta_pH <- ""
jar_History$delta_pH <- jar_History$Day00_pHiinsitu-jar_History$Day03_pHinsitu


```



##### Creating Hydrogen Concentration Numbers
```{r}

# function to calculate hydrogen ion concentration (ng/L) from pH
calcHfromPH <- function(pH){
  H <- 10^(-pH)
  H <- H *1000000000
  return(H)
}

calcPHfromH <- function(H){
  H <- H / 1000000000
  pH <- -log10(H)
  return(pH)
}

jar_History$HydroIons_Day03 <- ""
jar_History$HydroIons_Day03 <- calcHfromPH(jar_History$Day03_pHinsitu)

jar_History$HydroIons_Day00 <- ""
jar_History$HydroIons_Day00 <- calcHfromPH(jar_History$Day00_pHiinsitu)

jar_History$delta_HydroIons <- jar_History$HydroIons_Day03-jar_History$HydroIons_Day00


write.csv(jar_History, file = "jar_History.csv", row.names = FALSE)

```


#### 3.1) Plotting Hydrogen Ion Difference
```{r}

HydrogenIon_plot1 <- ggplot(jar_History, aes(unit_ID, delta_HydroIons)) +
            # geom_jitter(color = "grey") +
            geom_point(data = jar_History, 
                       aes(unit_ID, delta_HydroIons, colour = id_2)) +
            facet_wrap(~treatment) +
            xlab("Unit ID (Chamber Number)") +
            ylab("Change in Hydrogen Ion Concentration") +
            ggtitle("72 hour Hydrogen Concentration Difference") +
            ggeasy::easy_center_title() +
            theme_bw() 

HydrogenIon_plot1



centeredTitle_theme = theme(plot.title = 
element_text(hjust = 0.5))

HydrogenIon_plot1 + centeredTitle_theme


```


# Chamber 09 Plots 

```{r}

Chamber09jars = subset(jar_History, unit_ID == "Chamber_9")

CH09_pH_plot1 <- ggplot(Chamber09jars, aes(JarID, Day03_pHinsitu)) +
            # geom_jitter(color = "grey") +
            geom_point(data = Chamber09jars, 
                       aes(BottleID, Day00_pHiinsitu)) +
            geom_point(data = Chamber09jars, 
                       aes(JarID, Day03_pHinsitu, colour = id_2)) +
            facet_wrap(~treatment) +
            xlab("Jar and Bottle ID") +
            ylab("pH (measured at both Day03 & Day 00") +
            ggtitle("72 hour pH Bottle Jar Difference (CH09)") +
            theme_bw() 

CH09_pH_plot1

p9a <- CH09_pH_plot1 + theme(axis.text=element_text(size=5),
        axis.title=element_text(size=7,face="bold"))

p9a + theme(axis.text.x = element_text(angle = 30))

```

# Chamber 10 Plots 

```{r}

Chamber10jars = subset(jar_History, unit_ID  == "Chamber_10")

CH10_pH_plot1 <- ggplot(Chamber10jars, aes(JarID, Day03_pHinsitu)) +
            # geom_jitter(color = "grey") +
            geom_point(data = Chamber10jars, 
                       aes(BottleID, Day00_pHiinsitu)) +
            geom_point(data = Chamber10jars, 
                       aes(JarID, Day03_pHinsitu, colour = id_2)) +
            facet_wrap(~treatment) +
            xlab("Jar and Bottle ID") +
            ylab("pH (measured at both Day03 & Day 00") +
            ggtitle("72 hour pH Bottle Jar Difference (CH10)") +
            theme_bw() 

CH10_pH_plot1

p10 <- CH10_pH_plot1 + theme(axis.text=element_text(size=5),
        axis.title=element_text(size=7,face="bold"))

p10a<- p10 + theme(axis.text.x = element_text(angle = 30))
p10a

```

#### Comparing to other repeatability tests

```{r}

names(repeatability)
#  [1] "experiment"  "unit"        "unit_number" "id_1"        "id_2"        "id_3"        "time"        "date"       
#  [9] "salinity"    "pHat25"      "fileName"    "unit_ID"     "alk"         "insituTemp"  "pHinsitu"    "dateString" 
# [17] "treatName"   "treatpH"     "treatTemp"   "treatOther"  "dic"         "tankTemp"

names(rpt_cohort1)

rpt_cohort1to3 <- rbind(rpt_cohort1,
                    rpt_cohort2,  
                    rpt_cohort3)

rpt_cohorts <- merge(rpt_cohort1to3, rpt_map, by = "TRIS_ID")

calcHfromPH <- function(pH){
  H <- 10^(-pH)
  H <- H *1000000000
  return(H)
}

calcPHfromH <- function(H){
  H <- H / 1000000000
  pH <- -log10(H)
  return(pH)
}

rpt_cohorts$HydroIons_end <- ""
rpt_cohorts$HydroIons_end <- calcHfromPH(rpt_cohorts$pHinsitu_end)

rpt_cohorts$HydroIons_start <- ""
rpt_cohorts$HydroIons_start <- calcHfromPH(rpt_cohorts$pHinsitu_start)

rpt_cohorts$delta_HydroIons <- rpt_cohorts$HydroIons_start-rpt_cohorts$HydroIons_end

rpt_cohorts <- rpt_cohorts %>%
  dplyr::rename(TRIS_cohort = cohort.y)

HydrogenIon_TRISplot1 <- ggplot(rpt_cohorts, aes(id_1, delta_HydroIons)) +
            # geom_jitter(color = "grey") +
            geom_point(data = rpt_cohorts, 
                       aes(id_1, delta_HydroIons, colour = TRIS_cohort)) +
            facet_wrap(~Round) +
            xlab("Tris Round Number") +
            ylab("Change in Hydrogen Ion Concentration") +
            ggtitle("Hydrogen Concentration Difference") +
            ggeasy::easy_center_title() +
            theme_bw() 

HydrogenIon_TRISplot1 



centeredTitle_theme = theme(plot.title = 
element_text(hjust = 0.5))

HydrogenIon_TRISplot1 + centeredTitle_theme


```

Comparing the TRIS results. 


```{r}

calcHfromPH <- function(pH){
  H <- 10^(-pH)
  H <- H *1000000000
  return(H)
}

calcPHfromH <- function(H){
  H <- H / 1000000000
  pH <- -log10(H)
  return(pH)
}

IO_val$HydroIons_end <- ""
IO_val$HydroIons_end <- calcHfromPH(IO_val$pHinsitu_end)

IO_val$HydroIons_start <- ""
IO_val$HydroIons_start <- calcHfromPH(IO_val$pHinsitu_start)

IO_val$delta_HydroIons <- IO_val$HydroIons_start-IO_val$HydroIons_end


HydrogenIon_IOplot1 <- ggplot(IO_val, aes(id_1), delta_HydroIons) +
            geom_point(data = IO_val, 
                       aes(id_1, delta_HydroIons)) +
            # facet_wrap(~Round) +
            xlab("Instant Ocean Test (arbitrary groups)") +
            ylab("Change in Hydrogen Ion Concentration") +
            ggtitle("Hydrogen Concentration Difference (all samples compared to first IO sample)") +
            ggeasy::easy_center_title() +
            theme_bw() 

HydrogenIon_IOplot1 


```



```{r}

pH_IOplot1 <- ggplot(IO_val, aes(id_1), pHinsitu_end) +
            geom_point(data = IO_val, 
                       aes(id_1, pHinsitu_end)) +
            geom_point(data = IO_val, 
                       aes(id_1, pHinsitu_start)) +
            # facet_wrap(~Round) +
            xlab("Instant Ocean Test (arbitrary groups)") +
            ylab("Change in pH Between Samples") +
            ggtitle("pH Difference (all samples compared to first IO sample)") +
            ggeasy::easy_center_title() +
            theme_bw() 

pH_IOplot1

```




#### 3.2) Fun with Plots
```{r Fun with Plots by treatment}
# 
# jarTest.summary <- jarTest %>% group_by(treatment) %>%
#   dplyr::summarize(sd = sd(pHinsitu, na.rm = TRUE), 
#             mean = mean(pHinsitu, na.rm = TRUE), 
#             median = median(pHinsitu, na.rm = TRUE),
#             IQR = IQR(pHinsitu, na.rm = TRUE),
#             n = n()) %>%
#   mutate(se = sd/sqrt(n)) %>%
#   mutate(ci = se*1.96)
# jarTest.summary
# 
# 
# jarTest.summary_boxplot <- ggplot(jarTest, aes(treatment, pHinsitu)) +
#             # geom_jitter(color = "grey") +
#             geom_jitter(data = jarTest, aes(treatment, pHinsitu, colour = id_1)) +
#             geom_boxplot(notch = TRUE, outlier.shape = NA, colour = "green") +
#             geom_point(data = jarTest.summary, aes(x=treatment, y=mean), size=5, color = "purple") + 
#             geom_errorbar(data = jarTest.summary, 
#                           aes(x=treatment, y=mean, ymin = mean-sd, ymax = mean+sd), 
#                           color = "blue") +
#             geom_errorbar(data = jarTest.summary,
#                           aes(x=treatment, y=mean, ymin = mean-ci, ymax = mean+ci),
#                           colour = "red") +
#             # # facet_wrap(~placeholder) +
#             # xlab("Treatment") +
#             # ylab("non-Corrected pH") +
#             # ggtitle("pH insitu across treatments") +
#             theme_bw() 
# 
# jarTest.summary_boxplot
# 

# TODO were things mislabeled?
# need to only select bottles and then jars 

```






### 3.3) creating bottle cohort averages/constants
```{r}
# 
# unique(jarTest$BottleCohort)
#  # [1] "CH09_01"  "CH10_01"  "CH10_02"  "CH10_03"  "CH09_03"  "CH10_03a" "CH09_03a"
#  # [8] "CH09_04"  "CH10_04"  "CH09_02"  "N/A" 
# 
# # both chambers set to Low CO2 conditions 9/27/2021 to 9/30/2021
# # "LoCO2_30AUG21"
# LoCO2_treatment <- mean(subset(jarTest, id_3 == "LoCO2_30AUG21", select = c(pHinsitu))$pHinsitu)
# 
# # CH09_01 SPEC samples from 9/27/2021
# CH09_01start <- mean(subset(jarTest, id_3 == "CH09_01", select = c(pHinsitu))$pHinsitu)
# 
# # CH09_02 SPEC samples from 9/27/2021
# CH09_02start <- mean(subset(jarTest, id_3 == "CH09_02", select = c(pHinsitu))$pHinsitu)
# 
# 
# # CH10_01 SPEC samples from 9/27/2021
# CH10_01start <- mean(subset(jarTest, id_3 == "CH10_01", select = c(pHinsitu))$pHinsitu)
# 
# # CH10_02 SPEC samples from 9/27/2021
# CH10_02start <- mean(subset(jarTest, id_3 == "CH10_02", select = c(pHinsitu))$pHinsitu)
# 
# # CH09_03 SPEC samples from 9/27/2021
# CH09_03start <- mean(subset(jarTest, id_3 == "CH09_03", select = c(pHinsitu))$pHinsitu)
# 
# 
# # CH10_03 SPEC samples from 9/27/2021
# CH10_03start <- mean(subset(jarTest, id_3 == "CH10_03", select = c(pHinsitu))$pHinsitu)
# 
# # CH10_03a SPEC samples from 9/27/2021
# CH10_03astart <- mean(subset(jarTest, id_3 == "CH10_03a", select = c(pHinsitu))$pHinsitu)
# 
# 
# # CH09_04 SPEC samples from 9/27/2021
# CH09_04astart <- mean(subset(jarTest, id_3 == "CH09_04", select = c(pHinsitu))$pHinsitu)
# 
# # CH10_04 SPEC samples from 9/27/2021
# CH10_04astart <- mean(subset(jarTest, id_3 == "CH10_04", select = c(pHinsitu))$pHinsitu)



```




#### CH09_01 cohort plot
```{r}

# Subselect/select only observation with BottleCohort == "CH09_01"
## Add Y axis intercept = CH09_01start

# bc_ch09_01 = subset(jarTest, BottleCohort == "CH09_01")
# jarTest.CH09_01sum_plot <- ggplot(bc_ch09_01, aes(id_3, pHinsitu)) +
#             # geom_jitter(color = "grey") +
#             geom_point(data = bc_ch09_01, aes(id_3, pHinsitu)) +
#             geom_hline(yintercept = CH09_01start) +
#             facet_wrap(~id_2) +
#             # xlim(1,2) +
#             ylim(8.3, 7.2) +
#             # xlab("placeholder") +
#             # ylab("placeholder") +
#             ggtitle("72 hour Variation Between Source Bottle and Jar") +
#             theme_bw() 
# 
# jarTest.CH09_01sum_plot 

# jarTest.CH09_01sum_plot  + scale_y_reverse()


```





#### CH10_01 cohort plot
```{r}

# unique(jarTest$BottleCohort)
# 
# bc_ch10_01 = subset(jarTest, BottleCohort == "CH10_01")
# jarTest.CH10_01sum_plot <- ggplot(bc_ch10_01, aes(id_3, pHinsitu)) +
#             # geom_jitter(color = "grey") +
#             geom_point(data = bc_ch10_01, aes(id_3, pHinsitu)) +
#             geom_hline(yintercept = CH10_01start) +
#             facet_wrap(~id_2) +
#             # xlim(1,2) +
#             ylim(8.3, 7.2) +
#             # xlab("placeholder") +
#             # ylab("placeholder") +
#             ggtitle("72 hour Variation Between Source Bottle and Jar") +
#             theme_bw() 
# 
# jarTest.CH10_01sum_plot

```





#### CH09_02 cohort plot
```{r}

# bc_ch09_02 = subset(jarTest, BottleCohort == "CH09_02")
# jarTest.CH10_02sum_plot <- ggplot(bc_ch09_02, aes(id_3, pHinsitu)) +
#             # geom_jitter(color = "grey") +
#             geom_point(data = bc_ch09_02, aes(id_3, pHinsitu)) +
#             geom_hline(yintercept = CH09_02start) +
#             facet_wrap(~id_2) +
#             # xlim(1,2) +
#             ylim(8.3, 7.2) +
#             # xlab("placeholder") +
#             # ylab("placeholder") +
#             ggtitle("72 hour Variation Between Source Bottle and Jar (CH09_02") +
#             theme_bw() 
# 
# jarTest.CH10_02sum_plot

```









#### CH10_02 cohort plot
```{r}

# bc_ch10_02 = subset(jarTest, BottleCohort == "CH10_02")
# jarTest.CH10_02sum_plot <- ggplot(bc_ch10_02, aes(id_3, pHinsitu)) +
#             # geom_jitter(color = "grey") +
#             geom_point(data = bc_ch10_02, aes(id_3, pHinsitu)) +
#             geom_hline(yintercept = CH10_02start) +
#             facet_wrap(~id_2) +
#             # xlim(1,2) +
#             ylim(8.3, 7.2) +
#             # xlab("placeholder") +
#             # ylab("placeholder") +
#             ggtitle("72 hour Variation Between Source Bottle and Jar (CH10_02") +
#             theme_bw() 
# 
# jarTest.CH10_02sum_plot

```





#### CH09_03 cohort plot
```{r}

# unique(jarTest$BottleCohort)
# 
# bc_ch09_03 = subset(jarTest, BottleCohort == "CH09_03")
# jarTest.CH09_03sum_plot <- ggplot(bc_ch09_03, aes(id_3, pHinsitu)) +
#             # geom_jitter(color = "grey") +
#             geom_point(data = bc_ch09_03, aes(id_3, pHinsitu)) +
#             geom_hline(yintercept = CH09_03start) +
#             facet_wrap(~id_2) +
#             # xlim(1,2) +
#             ylim(8.3, 7.2) +
#             # xlab("placeholder") +
#             # ylab("placeholder") +
#             ggtitle("72 hour Variation Between Source Bottle and Jar") +
#             theme_bw() 
# 
# jarTest.CH09_03sum_plot

```




#### CH10_03 cohort plot
```{r}

# unique(jarTest$BottleCohort)
# 
# bc_ch10_03 = subset(jarTest, BottleCohort == "CH10_03")
# jarTest.CH10_03sum_plot <- ggplot(bc_ch10_03, aes(id_3, pHinsitu)) +
#             # geom_jitter(color = "grey") +
#             geom_point(data = bc_ch10_03, aes(id_3, pHinsitu)) +
#             geom_hline(yintercept = CH10_03start) +
#             facet_wrap(~id_2) +
#             # xlim(1,2) +
#             ylim(8.3, 7.2) +
#             # xlab("placeholder") +
#             # ylab("placeholder") +
#             ggtitle("72 hour Variation Between Source Bottle and Jar") +
#             theme_bw() 
# 
# jarTest.CH10_01sum_plot

```




#### CH09_03a cohort plot
```{r}

# unique(jarTest$BottleCohort)
# 
# bc_ch09_03a = subset(jarTest, BottleCohort == "CH09_03a")
# jarTest.CH09_03asum_plot <- ggplot(bc_ch09_03a, aes(id_3, pHinsitu)) +
#             # geom_jitter(color = "grey") +
#             geom_point(data = bc_ch09_03a, aes(id_3, pHinsitu)) +
#             geom_hline(yintercept = CH09_03astart) +
#             facet_wrap(~id_2) +
#             # xlim(1,2) +
#             ylim(8.3, 7.2) +
#             # xlab("placeholder") +
#             # ylab("placeholder") +
#             ggtitle("72 hour Variation Between Source Bottle and Jar") +
#             theme_bw() 
# 
# jarTest.CH09_03asum_plot 

```



#### CH10_03a cohort plot
```{r}

# unique(jarTest$BottleCohort)
# 
# bc_ch10_03a = subset(jarTest, BottleCohort == "CH10_03a")
# jarTest.CH10_03asum_plot <- ggplot(bc_ch10_03a, aes(id_3, pHinsitu)) +
#             # geom_jitter(color = "grey") +
#             geom_point(data = bc_ch10_03a, aes(id_3, pHinsitu)) +
#             geom_hline(yintercept = CH10_03astart) +
#             facet_wrap(~id_2) +
#             # xlim(1,2) +
#             ylim(8.3, 7.2) +
#             # xlab("placeholder") +
#             # ylab("placeholder") +
#             ggtitle("72 hour Variation Between Source Bottle and Jar") +
#             theme_bw() 
# 
# jarTest.CH10_03asum_plot 

```






#### CH09_04 cohort plot
```{r}

# unique(jarTest$BottleCohort)
# 
# bc_ch09_04 = subset(jarTest, BottleCohort == "CH09_04")
# jarTest.CH09_04sum_plot <- ggplot(bc_ch09_04, aes(id_3, pHinsitu)) +
#             # geom_jitter(color = "grey") +
#             geom_point(data = bc_ch09_04, aes(id_3, pHinsitu)) +
#             geom_hline(yintercept = CH09_04start) +
#             facet_wrap(~id_2) +
#             # xlim(1,2) +
#             ylim(8.3, 7.2) +
#             # xlab("placeholder") +
#             # ylab("placeholder") +
#             ggtitle("72 hour Variation Between Source Bottle and Jar") +
#             theme_bw() 
# 
# jarTest.CH09_04sum_plot

```



#### CH09_04a cohort plot
```{r}

# unique(jarTest$BottleCohort)
# 
# bc_ch09_04a = subset(jarTest, BottleCohort == "CH09_04a")
# jarTest.CH09_04asum_plot <- ggplot(bc_ch09_04a, aes(id_3, pHinsitu)) +
#             # geom_jitter(color = "grey") +
#             geom_point(data = bc_ch09_04a, aes(id_3, pHinsitu)) +
#             geom_hline(yintercept = CH09_04astart) +
#             facet_wrap(~id_2) +
#             # xlim(1,2) +
#             ylim(8.3, 7.2) +
#             # xlab("placeholder") +
#             # ylab("placeholder") +
#             ggtitle("72 hour Variation Between Source Bottle and Jar") +
#             theme_bw() 
# 
# jarTest.CH09_04asum_plot 

```




#### CH10_04a cohort plot
```{r}

# unique(jarTest$BottleCohort)
# 
# bc_ch10_04a = subset(jarTest, BottleCohort == "CH10_04a")
# jarTest.CH10_04asum_plot <- ggplot(bc_ch10_04a, aes(id_3, pHinsitu)) +
#             # geom_jitter(color = "grey") +
#             geom_point(data = bc_ch10_04a, aes(id_3, pHinsitu)) +
#             geom_hline(yintercept = CH10_04astart) +
#             facet_wrap(~id_2) +
#             # xlim(1,2) +
#             ylim(8.3, 7.2) +
#             # xlab("placeholder") +
#             # ylab("placeholder") +
#             ggtitle("72 hour Variation Between Source Bottle and Jar") +
#             theme_bw() 
# 
# jarTest.CH10_04asum_plot 

```




#### CH10_04 cohort plot
```{r}

# unique(jarTest$BottleCohort)
# 
# bc_ch10_04 = subset(jarTest, BottleCohort == "CH10_04")
# jarTest.CH10_04sum_plot <- ggplot(bc_ch10_04, aes(id_3, pHinsitu)) +
#             # geom_jitter(color = "grey") +
#             geom_point(data = bc_ch10_04, aes(id_3, pHinsitu)) +
#             geom_hline(yintercept = CH10_04start) +
#             facet_wrap(~id_2) +
#             # xlim(1,2) +
#             ylim(8.3, 7.2) +
#             # xlab("placeholder") +
#             # ylab("placeholder") +
#             ggtitle("72 hour Variation Between Source Bottle and Jar") +
#             theme_bw() 
# 
# jarTest.CH10_04sum_plot 

```


## By Chamber, 72 hour Variation Between Source Bottle and Jar
```{r}

# ggplot(jarTest, aes(id_3, pHinsitu)) +
#             # geom_jitter(color = "grey") +
#             geom_point(data = jarTest, aes(id_3, pHinsitu)) +
#             geom_hline(yintercept = CH09_01start) +
#             geom_hline(yintercept = CH09_02start) +
#             geom_hline(yintercept = CH09_03start) +
#             geom_hline(yintercept = CH09_04astart) +
#               # xlim(1,2) +
#             geom_hline(yintercept = CH10_01start) +
#             geom_hline(yintercept = CH10_02start) +
#             geom_hline(yintercept = CH10_03start) +
#             geom_hline(yintercept = CH10_03astart) +
#             geom_hline(yintercept = CH10_04astart) +
#             facet_wrap(~unit_number) +
#             # xlim(1,2) +
#             ylim(8.3, 7.2) +
#             # xlab("placeholder") +
#             # ylab("placeholder") +
#             ggtitle("72 hour Variation Between Source Bottle and Jar") +
#             theme_bw() 


```



## By Chamber, 72 hour Variation Between Source Bottle and Jar by Treatment
```{r}

# ggplot(jarTest, aes(treatment, pHinsitu)) +
#             # geom_jitter(color = "grey") +
#             geom_point(data = jarTest, aes(treatment, pHinsitu, colour=id_2)) +
#             geom_hline(yintercept = CH09_01start) +
#             geom_hline(yintercept = CH09_02start) +
#             geom_hline(yintercept = CH09_03start) +
#             geom_hline(yintercept = CH09_04astart) +
#               # xlim(1,2) +
#             geom_hline(yintercept = CH10_01start) +
#             geom_hline(yintercept = CH10_02start) +
#             geom_hline(yintercept = CH10_03start) +
#             geom_hline(yintercept = CH10_03astart) +
#             geom_hline(yintercept = CH10_04astart) +
#   
#             geom_hline(yintercept = LoCO2_treatment) +
#   
#             facet_wrap(~unit_number) +
#             # xlim(1,2) +
#             ylim(8.3, 7.2) +
#             # xlab("placeholder") +
#             # ylab("placeholder") +
#             ggtitle("72 hour Variation Between Source Bottle and Jar") +
#             theme_bw() 
# 

```



# 4.) Can Kate Case_When 
```{r}

# jarTest$TreatmentCatagory <- ""
# jarTest$TreatmentCatagory <- "placeholder"
# 
# jarTest$Container_ID <- ""
# jarTest$Container_ID <- "placeholder"
# 
# jarTest$Container_Cohort <- ""
# jarTest$Container_Cohort <- "placeholder"
# 
# # want Treatment category to be as follows:
# # HiCO2 if ID_1 was "jar" 
# #                   and collected on 8/30/21 
# #                   and unit_ID was "Chamber_10"
# # MidCO2 if ID_1 was "jar" 
# #                   and collected on 8/30/21 
# #                   and unit_ID was "Chamber_09"
# # LoCO2 if ID_1 was "bottle"
#                     # and was collected on 8/30/21
# 
# 
# 
# 
# # bring in HiCO2
# jarTest <- mutate(jarTest, TreatmentCategory = case_when(
#                                       (jarTest$id_1 == "Jar") &
#                                       (jarTest$date == as.POSIXct("2021-08-30")) &
#                                       (jarTest$unit_ID == "Chamber_10")  ~ "HiCO2",
#                                       
#                                       (jarTest$id_1 == "Jar") &
#                                       (jarTest$date == as.POSIXct("2021-08-30")) &
#                                       (jarTest$unit_ID == "Chamber_9")  ~ "MidCO2",   
#                                       
#                                       (jarTest$id_1 == "Bottle") &
#                                       (jarTest$date == "2021-08-30") ~ "LoCO2",                          
#                                       TRUE ~"other"
#                                         )
#                                       )
# 
# # # testing only against one variable
# # if_else()
# 
# as.POSIXct("2021-08-30")
# 
#            
# # bring in MidCO2
# mutate(jarTest$TreatmentCatagory = case_when(
#                                       (jarTest$id_1 == "Jar")
#                                       & (jarTest$date == "2021-08-27") 
#                                       & (jarTest$unit_ID == "Chamber_9")  ~ "MidCO2",                          
#                                       TRUE ~"other"
#                                         )
#                                       )
# 
# # bring in LoCO2
# mutate(jarTest$TreatmentCatagory = case_when(
#                                       (jarTest$id_1 == "Bottle")
#                                       & (jarTest$date == "2021-08-30") ~ "LoCO2",                          
#                                       TRUE ~"other"
#                                         )
#                                       )
# 
# 
# 
# rename(jarTest, id_3 = Jar_ID)
# rename(jarMap, JarID = Jar_ID)
# 
# jarTest <- jarTest %>%
#   dplyr::rename(id_3 = Jar_ID)
# 
# jarTest <- jarTest %>%
#   rename(Jar_ID = id_3) %>%
#   full_join(jarMAP)
# 
# 
# CTD_log_0623_clean <- CTD_log_0623 %>%
#   dplyr::rename(new_temperature = temperature)
# 
# dTankCNDCT <- merge(UDACNDCT, SPECCNDCT, all = TRUE)
# 
# jarTEST_SPEC <- merge(jarTest, jarMap, by = JarID id_3)
# 
# 
# 
# 


# # Example from Paul's PNX code on transfer sheets:
# for(i in 1:length(trans_files)){
#    new_filename <- paste(word(word(trans_files[i], -1 ,sep = "/"), sep = ".csv"), "_recode.csv", sep = "")
#   d_top <- read_csv(trans_files[i], n_max = 2)
#   d_bot <- read_csv(trans_files[i], skip = 2) %>%
#     mutate(Molt = case_when(Molt == "z" ~ "zoea",
#                             Molt %in% c("x", "X", "Molt") ~ "meg",
#                             Molt %in% c("MEG", "meg", "M") ~ "meg",
#                             Molt %in% c("JUV", "J") ~ "juv",
#                             is.na(Molt) ~ NA_character_,
#                             TRUE ~ "other")) %>%
#     #correct some ambiguous molt scoring (e.g. "X")
#     mutate(Molt = case_when(crabID == "CH09_CRN_134_2019_06_05" &
#                               new_filename == "TransferCrab_CH09.2019.06.26_recode.csv" ~ "meg",
#            crabID == "CH10_CRN_135_2019_06_05" &
#                               new_filename == "TransferCrab_CH10.2019.06.17_recode.csv" ~ "juv",
#            crabID == "CH10_CRN_145_2019_06_05" &
#                               new_filename == "TransferCrab_CH10.2019.06.17_recode.csv" ~ "juv",
#            TRUE ~ Molt)) %>%
#     mutate(Dead = if_else(is.na(Dead), NA_character_, "dead")) %>%
#     mutate(Remov = case_when(Remov %in% 
#                                c("R","X", "moved_to_poop_study", "removed_to_poop_study") ~
#                                "removed",
#            Remov %in% c("pickled", "PICKLED") ~ "preserved",
#            is.na(Remov) ~ NA_character_,
#           TRUE ~ "other")) %>%
#     mutate(Lost = case_when(Lost %in% c("X", "lost", "Lost", "LOST") ~ "lost",
#                             Lost == "chamber_failure" ~ "chamber_failure",
#                             is.na(Lost) ~ NA_character_,
#                             TRUE ~ "other")) %>%
#       {.}
#    
#     write_csv(d_top, here("data_raw", "well_plate_data_corrected_recode", new_filename), na = "")
#     write_csv(d_bot, here("data_raw", "well_plate_data_corrected_recode", new_filename), na = "", 
#               append = TRUE)
# }




```



# 5.) Jar Test Summary
```{r  Jar Test Summary}

# jarTest$pH_of_sample_without_correction <- as.numeric(jarTest$pH_of_sample_without_correction)
# 
# 
# jarTest.summary <- jarTest %>% group_by(Treatment) %>%
#   dplyr::summarize(sd = sd(pH_of_sample_without_correction, na.rm = TRUE), 
#             mean = mean(pH_of_sample_without_correction, na.rm = TRUE), 
#             median = median(pH_of_sample_without_correction, na.rm = TRUE),
#             IQR = IQR(pH_of_sample_without_correction, na.rm = TRUE),
#             n = n()) %>%
#   mutate(se = sd/sqrt(n)) %>%
#   mutate(ci = se*1.96)
# jarTest.summary
# 
# 
# jarTest.summary_boxplot <- ggplot(jarTest, aes(Treatment, pH_of_sample_without_correction)) +
#             # geom_jitter(color = "grey") +
#             geom_jitter(data = jarTest, aes(Treatment, pH_of_sample_without_correction)) +
#             geom_boxplot(notch = TRUE, outlier.shape = NA, colour = "green") +
#             geom_point(data = jarTest.summary, aes(x=Treatment, y=mean), size=5, color = "purple") + 
#             geom_errorbar(data = jarTest.summary, 
#                           aes(x=Treatment, y=mean, ymin = mean-sd, ymax = mean+sd), 
#                           color = "blue") +
#             geom_errorbar(data = jarTest.summary,
#                           aes(x=Treatment, y=mean, ymin = mean-ci, ymax = mean+ci),
#                           colour = "red") +
#             # # facet_wrap(~placeholder) +
#             # xlab("Treatment") +
#             # ylab("non-Corrected pH") +
#             # ggtitle("non Temperature Corrected pH across Brands") +
#             theme_bw() 
# 
# jarTest.summary_boxplot

# kable(jarTest.summary, digits = 4)
# write.csv(jarTest.summary, "ISO_KRL_jarTest.summary.csv")


```




### 5.1) Jar Test Plots
```{r Jar test plots}

# Creating four separate means from the blank vials per trial

x1 <- droplevels(filter(jarTest, Manufacturer != "N/A"))

x1.jarTest.summary <- x1 %>% group_by(Treatment) %>%
  dplyr::summarize(sd = sd(pH_of_sample_without_correction, na.rm = TRUE), 
            mean = mean(pH_of_sample_without_correction, na.rm = TRUE), 
            median = median(pH_of_sample_without_correction, na.rm = TRUE),
            IQR = IQR(pH_of_sample_without_correction, na.rm = TRUE),
            n = n()) %>%
  mutate(se = sd/sqrt(n)) %>%
  mutate(ci = se*1.96)
x1.jarTest.summary 


jarTest.summary_boxplot2 <- ggplot(jarTest, aes(Treatment, pH_of_sample_without_correction)) +
            # geom_jitter(color = "grey") +
            # geom_jitter(data = jarTest, aes(Treatment, pH_of_sample_without_correction)) +
            geom_jitter(aes(colour = Manufacturer)) +
            
            # # facet_wrap(~TrialID) +
            # xlab("Treatment") +
            # ylab("µg O2 h -1 g -1") +
            # ggtitle("Corrected Slope Summary Plot") +
            theme_bw() 

jarTest.summary_boxplot2



jarTest.summary_boxplot3 <- ggplot(jarTest, aes(Treatment, pH_of_sample_without_correction)) +
            # geom_jitter(color = "grey") +
            # geom_jitter(data = jarTest, aes(Treatment, pH_of_sample_without_correction)) +
            geom_jitter(aes(colour = insertType)) +
            
            # # facet_wrap(~TrialID) +
            # xlab("Treatment") +
            # ylab("µg O2 h -1 g -1") +
            # ggtitle("Corrected Slope Summary Plot") +
            theme_bw() 

jarTest.summary_boxplot3



```



5.) jarTest results & Summary

```{r  jarTest_Test Summary}

jarTest$pHinsitu <- as.numeric(jarTest$pHinsitu)


jarTest.summary <- jarTest %>% group_by(Treatment) %>%
  dplyr::summarize(sd = sd(pHinsitu, na.rm = TRUE), 
            mean = mean(pHinsitu, na.rm = TRUE), 
            median = median(pHinsitu, na.rm = TRUE),
            IQR = IQR(pHinsitu, na.rm = TRUE),
            n = n()) %>%
  mutate(se = sd/sqrt(n)) %>%
  mutate(ci = se*1.96)
jarTest.summary


jarTest.summary_boxplot <- ggplot(jarTest, aes(Treatment, pH_of_sample_without_correction)) +
            # geom_jitter(color = "grey") +
            geom_jitter(data = jarTest, aes(Treatment, pH_of_sample_without_correction)) +
            geom_boxplot(notch = TRUE, outlier.shape = NA, colour = "green") +
            geom_point(data = jarTest.summary, aes(x=Treatment, y=mean), size=5, color = "purple") + 
            geom_errorbar(data = jarTest.summary, 
                          aes(x=Treatment, y=mean, ymin = mean-sd, ymax = mean+sd), 
                          color = "blue") +
            geom_errorbar(data = jarTest.summary,
                          aes(x=Treatment, y=mean, ymin = mean-ci, ymax = mean+ci),
                          colour = "red") +
            # # facet_wrap(~placeholder) +
            # xlab("Treatment") +
            # ylab("non-Corrected pH") +
            # ggtitle("non Temperature Corrected pH across Brands") +
            theme_bw() 

jarTest.summary_boxplot

kable(jarTest.summary, digits = 4)
write.csv(jarTest.summary, "ISO_KRL_jarTest.summary.csv")



```{r}
#**************E*N*D*************# 
#*********************************
## END OF SCRIPT | END OF DOCUMENT 
#*********************************
```


## END OF SCRIPT | END OF DOCUMENT







