
---
title: "Jar leak Test"
output:
 html_document:
    df_print: paged
    code_folding: hide
    toc: TRUE
    toc_depth: 4
    toc_float: true
    theme: cerulean
    highlight: haddock
    smart: false
editor_options: 
  chunk_output_type: inline
---


Hello World

Author: OA Lab, NWFSC
Title: Reading Meta data for Krill Towing Data
Date: September 2021


# Version Check
```{r 0.1 Version Check , echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
## Version Check
#********************************* 
R.version

```



# 1.) Libraries
```{r 0.0 Libraries , echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
##Libraries
#********************************* 
library(stringr)
library(tidyverse)
library(plyr)
library(nlme)
library(tidyr)
library(dbplyr)
library(dplyr)
library(purrr)
library(wql)
library(lubridate)
library(tibbletime)
#for graphing
library(ggplot2)
library(ggeasy)
library(ggfortify)
library(stringr)
library(nlme)
library(RColorBrewer)
library(patchwork)
#statistical analysis
# library(gdata)
# library(rsq)
# library(doBy)
# library(lme4)
# library(lmerTest)
#Rnotebooks 
library(gridExtra)
library(kableExtra)
library(todor)
library(knitr)
#metadata
library(metacsv)
#Hydrogen concentration
library(seacarb)

```



# 2.) Creating Dataframes and new CSV documents 
```{r Creating Dataframes and new CSV documents }

#*********************************
## 2.) Creating Dataframes and new CSV documents
#*********************************

jarTest <- read_csv(here::here("raw_Data", "jarLeak", "SpecData_Cohort_1_to_8_Day00Day03.csv"))
bottleMAP <- read_csv(here::here("raw_Data", "jarLeak", "BottleSalinityMap.csv"))
jarMAP <- read_csv(here::here("raw_Data", "jarLeak", "jarBottleMap.csv"))

repeatability <- read_csv(here::here("Data", "SpecData_Repeatability_compare.csv"))
rpt_cohort1 <- read_csv(here::here("Data", "TRISround1_round2_cohort1.csv"))
rpt_cohort2 <- read_csv(here::here("Data", "TRISround1_round2_cohort2.csv"))
rpt_cohort3 <- read_csv(here::here("Data", "TRISround1_round2_cohort3.csv"))
rpt_map <- read_csv(here::here("Data", "TRISmap.csv"))

IO_val <- read_csv(here::here("Data", "InstantOceanValidations.csv"))

Hydrogen_History <- read_csv(here::here("Data", "Hydrogen_History.csv"))


```



# 3.) Data cleaning
Key points: 14 jars per Chamber
28x2 Jar Observations should be recorded
56 observations total

```{r Jar Test Cleaning}
#*********************************
## 3.) Jar Test Cleaning
#*********************************

jarTest$date <- as.POSIXct(jarTest$date, format="%m/%d/%y")
names(jarTest)
#  [1] "experiment"  "unit"        "unit_number" "id_1"        "id_2"        "id_3"        "time"        "date"       
#  [9] "salinity"    "pHat25"      "fileName"    "unit_ID"     "alk"         "insituTemp"  "pHinsitu"    "dateString" 
# [17] "treatName"   "treatpH"     "treatTemp"   "treatOther"  "dic"         "tankTemp"    "JarID"       "treatment"

# jarTest columns of interest
#  [1]  "unit"     "unit_number" "id_1"        "id_2"        "id_3"       "date"
#  [7] "salinity    "unit_ID"      "pHinsitu"     "JarID"       "treatment"
# 11 items of interest

# Jar SPEC Subelection Time!
jar_SPEC <- subset(jarTest, select = -c(experiment,
                                               time, 
                                              pHat25,
                                              fileName,
                                              treatName,
                                              treatpH, 
                                              alk,
                                              insituTemp,
                                              dateString,
                                              treatName,
                                              treatpH,
                                              treatTemp,
                                              treatOther,
                                              dic))

#Jar Map cleaning
names(jarMAP)
 # [1] "SEQ"            "Manufacturer"   "CHMBR"          "BottleTime"    
 # [5] "BottleDate"     "BottleNumber"   "JarID"          "insert"        
 # [9] "Manufacturer_1" "Treatment"

#Creating at least 6 column file -  Creating a Jar History File
# column 1 JarID
# column 2 Source Bottle
# column 3 Bottle pH Day 00
# column 4 Bootle pH Day 03
# column 5 delta of pH
# column 6 Jar Description (manufacturer and insert)

jar_History <- merge(jar_SPEC, jarMAP, by = "JarID")
# loss of observation by dropping bottles

names(jar_History)
 
# jarTest <- jarTest %>%
#   dplyr::rename(BottleID = BottleCohort)

jar_History <- jar_History %>%
  dplyr::rename(BottleID = BottleNumber)


# bottle_pH <- subset(jarTest, id_1 == "Bottle", select = c(BottleID, 
#                                                           pHinsitu))
# bottle_History <- merge(bottle_pH, bottleMAP, by = "BottleID")

jar_History <- merge(jar_History, bottleMAP, by = "BottleID")


names(jar_History)
#  [1] "BottleID"          "JarID"             "unit"              "unit_number"       "id_1"             
#  [6] "id_2"              "id_3"              "date"              "salinity"          "unit_ID"          
# [11] "pHinsitu"          "tankTemp"          "treatment"         "SEQ"               "Manufacturer"     
# [16] "CHMBR"             "BottleTime"        "BottleDate"        "insert"            "Manufacturer_1"   
# [21] "Treatment.x"       "SourceSalinity"    "BubbleEndSalinity" "Treatment.x"       "Day00_pHiinsitu"  
# [26] "X6"                "X7"                "X8"                "X9"                "X10"              
# [31] "X11"               "X12"               "X13"              

# #Cleaning if any of jar history
jar_History <- subset(jar_History, select = -c(tankTemp,
                                               Treatment.x,
                                              Treatment.x,
                                              X6,
                                              X7,
                                              X8,
                                              X9,
                                              X10,
                                              X11,
                                              X12,
                                              X13))

jar_History <- jar_History %>%
  dplyr::rename(Day03_pHinsitu = pHinsitu)


jar_History$delta_pH <- ""
jar_History$delta_pH <- jar_History$Day00_pHiinsitu-jar_History$Day03_pHinsitu


```



##### Creating Hydrogen Concentration Numbers
```{r}

# function to calculate hydrogen ion concentration (ng/L) from pH
calcHfromPH <- function(pH){
  H <- 10^(-pH)
  H <- H *1000000000
  return(H)
}

calcPHfromH <- function(H){
  H <- H / 1000000000
  pH <- -log10(H)
  return(pH)
}

jar_History$HydroIons_Day03 <- ""
jar_History$HydroIons_Day03 <- calcHfromPH(jar_History$Day03_pHinsitu)

jar_History$HydroIons_Day00 <- ""
jar_History$HydroIons_Day00 <- calcHfromPH(jar_History$Day00_pHiinsitu)

jar_History$delta_HydroIons <- jar_History$HydroIons_Day03-jar_History$HydroIons_Day00


write.csv(jar_History, file = "jar_History.csv", row.names = FALSE)

```


#### 3.1) Plotting Hydrogen Ion Difference
```{r}

HydrogenIon_plot1 <- ggplot(jar_History, aes(unit_ID, delta_HydroIons)) +
            # geom_jitter(color = "grey") +
            geom_point(data = jar_History, 
                       aes(unit_ID, delta_HydroIons, colour = id_2)) +
            facet_wrap(~treatment) +
            xlab("Unit ID (Chamber Number)") +
            ylab("Change in Hydrogen Ion Concentration") +
            ggtitle("72 hour Hydrogen Concentration Difference") +
            ggeasy::easy_center_title() +
            theme_bw() 

HydrogenIon_plot1



centeredTitle_theme = theme(plot.title = 
element_text(hjust = 0.5))

HydrogenIon_plot1 + centeredTitle_theme


```


# Chamber 09 Plots 

```{r}

Chamber09jars = subset(jar_History, unit_ID == "Chamber_9")

CH09_pH_plot1 <- ggplot(Chamber09jars, aes(JarID, Day03_pHinsitu)) +
            # geom_jitter(color = "grey") +
            geom_point(data = Chamber09jars, 
                       aes(BottleID, Day00_pHiinsitu)) +
            geom_point(data = Chamber09jars, 
                       aes(JarID, Day03_pHinsitu, colour = id_2)) +
            facet_wrap(~treatment) +
            xlab("Jar and Bottle ID") +
            ylab("pH (measured at both Day03 & Day 00") +
            ggtitle("72 hour pH Bottle Jar Difference (CH09)") +
            theme_bw() 

CH09_pH_plot1

p9a <- CH09_pH_plot1 + theme(axis.text=element_text(size=5),
        axis.title=element_text(size=7,face="bold"))

p9a + theme(axis.text.x = element_text(angle = 30))

```

# Chamber 10 Plots 

```{r}

Chamber10jars = subset(jar_History, unit_ID  == "Chamber_10")

CH10_pH_plot1 <- ggplot(Chamber10jars, aes(JarID, Day03_pHinsitu)) +
            # geom_jitter(color = "grey") +
            geom_point(data = Chamber10jars, 
                       aes(BottleID, Day00_pHiinsitu)) +
            geom_point(data = Chamber10jars, 
                       aes(JarID, Day03_pHinsitu, colour = id_2)) +
            facet_wrap(~treatment) +
            xlab("Jar and Bottle ID") +
            ylab("pH (measured at both Day03 & Day 00") +
            ggtitle("72 hour pH Bottle Jar Difference (CH10)") +
            theme_bw() 

CH10_pH_plot1

p10 <- CH10_pH_plot1 + theme(axis.text=element_text(size=5),
        axis.title=element_text(size=7,face="bold"))

p10a<- p10 + theme(axis.text.x = element_text(angle = 30))
p10a

```

#### Comparing to other repeatability tests

```{r}

names(repeatability)
#  [1] "experiment"  "unit"        "unit_number" "id_1"        "id_2"        "id_3"        "time"        "date"       
#  [9] "salinity"    "pHat25"      "fileName"    "unit_ID"     "alk"         "insituTemp"  "pHinsitu"    "dateString" 
# [17] "treatName"   "treatpH"     "treatTemp"   "treatOther"  "dic"         "tankTemp"

names(rpt_cohort1)

rpt_cohort1to3 <- rbind(rpt_cohort1,
                    rpt_cohort2,  
                    rpt_cohort3)

rpt_cohorts <- merge(rpt_cohort1to3, rpt_map, by = "TRIS_ID")

calcHfromPH <- function(pH){
  H <- 10^(-pH)
  H <- H *1000000000
  return(H)
}

calcPHfromH <- function(H){
  H <- H / 1000000000
  pH <- -log10(H)
  return(pH)
}

rpt_cohorts$HydroIons_end <- ""
rpt_cohorts$HydroIons_end <- calcHfromPH(rpt_cohorts$pHinsitu_end)

rpt_cohorts$HydroIons_start <- ""
rpt_cohorts$HydroIons_start <- calcHfromPH(rpt_cohorts$pHinsitu_start)

rpt_cohorts$delta_HydroIons <- rpt_cohorts$HydroIons_start-rpt_cohorts$HydroIons_end

rpt_cohorts <- rpt_cohorts %>%
  dplyr::rename(TRIS_cohort = cohort.y)

HydrogenIon_TRISplot1 <- ggplot(rpt_cohorts, aes(id_1, delta_HydroIons)) +
            # geom_jitter(color = "grey") +
            geom_point(data = rpt_cohorts, 
                       aes(id_1, delta_HydroIons, colour = TRIS_cohort)) +
            facet_wrap(~Round) +
            xlab("Tris Round Number") +
            ylab("Change in Hydrogen Ion Concentration") +
            ggtitle("Hydrogen Concentration Difference") +
            ggeasy::easy_center_title() +
            theme_bw() 

HydrogenIon_TRISplot1 



centeredTitle_theme = theme(plot.title = 
element_text(hjust = 0.5))

HydrogenIon_TRISplot1 + centeredTitle_theme


```

Comparing the TRIS results. 


```{r}

calcHfromPH <- function(pH){
  H <- 10^(-pH)
  H <- H *1000000000
  return(H)
}

calcPHfromH <- function(H){
  H <- H / 1000000000
  pH <- -log10(H)
  return(pH)
}

IO_val$HydroIons_end <- ""
IO_val$HydroIons_end <- calcHfromPH(IO_val$pHinsitu_end)

IO_val$HydroIons_start <- ""
IO_val$HydroIons_start <- calcHfromPH(IO_val$pHinsitu_start)

IO_val$delta_HydroIons <- IO_val$HydroIons_start-IO_val$HydroIons_end


HydrogenIon_IOplot1 <- ggplot(IO_val, aes(id_1), delta_HydroIons) +
            geom_point(data = IO_val, 
                       aes(id_1, delta_HydroIons)) +
            # facet_wrap(~Round) +
            xlab("Instant Ocean Test (arbitrary groups)") +
            ylab("Change in Hydrogen Ion Concentration") +
            ylim(-4, 7) +
            ggtitle("Hydrogen Concentration Difference (all samples compared to first IO sample)") +
            ggeasy::easy_center_title() +
            theme_bw() 

HydrogenIon_IOplot1 




```



```{r}

IO_val$pHmean <- ""
IO_val$pHmean <- mean(IO_val$pHinsitu_end)


IO_val$HydroIons_end <- ""
IO_val$HydroIons_end <- calcHfromPH(IO_val$pHinsitu_end)

IO_val$HydroIons_average <- ""
IO_val$HydroIons_average <- calcHfromPH(IO_val$pHmean)

IO_val$chg_HydroIons <- IO_val$HydroIons_average-IO_val$HydroIons_end

 # IO_val %>% ggplot(data=.)+geom_histogram(aes(x=chg_HydroIons), binwidth = .05)
 
 
 ggplot(data=IO_val, aes(IO_val$chg_HydroIons)) + 
  geom_histogram() + 
   ylab("Change in Hydrogen Ion Concentration from 24 Sample Mean") +
   ggtitle("Hydrogen Concentration Difference From Mean") +
  ggeasy::easy_center_title() +
  theme_bw() 
 
```



```{r}

pH_IOplot1 <- ggplot(IO_val, aes(id_1), pHinsitu_end) +
            geom_point(data = IO_val, 
                       aes(id_1, pHinsitu_end)) +
            geom_point(data = IO_val, 
                       aes(id_1, pHinsitu_start)) +
            # facet_wrap(~Round) +
            xlab("Instant Ocean Test (arbitrary groups)") +
            ylab("Change in pH Between Samples") +
            ggtitle("pH Difference (all samples compared to first IO sample)") +
            ggeasy::easy_center_title() +
            theme_bw() 

pH_IOplot1

```



```{r}



 ggplot(data=Hydrogen_History, aes(Hydrogen_History$H_percentChg)) + 
  geom_histogram() + 
   ylab("Hydrogen Ion Change (Percent)") +
   ggtitle("Hydrogen Ion Change Compared to Concentration Overall") +
  ggeasy::easy_center_title() +
  theme_bw()


Hydrogen_History$unit_number <- as.character(Hydrogen_History$unit_number)

Hydrogen_plot2 <- ggplot(Hydrogen_History, aes(unit_number, H_percentChg)) +
            # geom_jitter(color = "grey") +
            geom_point(data = Hydrogen_History, 
                       aes(unit_number, H_percentChg, colour = id_2)) +
            facet_wrap(~treatment) +
            xlab("Unit ID (Chamber Number)") +
            ylab("Percent Change in Hydrogen Ion Concentration") +
            ggtitle("72 hour Hydrogen Concentration Percent Change") +
            ggeasy::easy_center_title() +
            theme_bw() 

Hydrogen_plot2


```








#### 3.2) Fun with Plots
```{r Fun with Plots by treatment}
# 
# jarTest.summary <- jarTest %>% group_by(treatment) %>%
#   dplyr::summarize(sd = sd(pHinsitu, na.rm = TRUE), 
#             mean = mean(pHinsitu, na.rm = TRUE), 
#             median = median(pHinsitu, na.rm = TRUE),
#             IQR = IQR(pHinsitu, na.rm = TRUE),
#             n = n()) %>%
#   mutate(se = sd/sqrt(n)) %>%
#   mutate(ci = se*1.96)
# jarTest.summary
# 
# 
# jarTest.summary_boxplot <- ggplot(jarTest, aes(treatment, pHinsitu)) +
#             # geom_jitter(color = "grey") +
#             geom_jitter(data = jarTest, aes(treatment, pHinsitu, colour = id_1)) +
#             geom_boxplot(notch = TRUE, outlier.shape = NA, colour = "green") +
#             geom_point(data = jarTest.summary, aes(x=treatment, y=mean), size=5, color = "purple") + 
#             geom_errorbar(data = jarTest.summary, 
#                           aes(x=treatment, y=mean, ymin = mean-sd, ymax = mean+sd), 
#                           color = "blue") +
#             geom_errorbar(data = jarTest.summary,
#                           aes(x=treatment, y=mean, ymin = mean-ci, ymax = mean+ci),
#                           colour = "red") +
#             # # facet_wrap(~placeholder) +
#             # xlab("Treatment") +
#             # ylab("non-Corrected pH") +
#             # ggtitle("pH insitu across treatments") +
#             theme_bw() 
# 
# jarTest.summary_boxplot
# 

# TODO were things mislabeled?
# need to only select bottles and then jars 

```








#**************E*N*D*************# 
#*********************************
## END OF SCRIPT | END OF DOCUMENT 
#*********************************
```


## END OF SCRIPT | END OF DOCUMENT



